Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Reshuffle results section and add linear regression notes

We used a Bayesian ordinal hierarchical regression model to quantify the influence of reef
characteristics on reef cluster assignment. Using Turing.jl [@fjelde2025] we model the
influence of five predictors, median depth, log total connectivity strength, log source to
sink ratio, mean DHW, log reef area and mean DHW tolerance level on cluster assignment,
including random intercepts for levels of **bioregion** and GCM identity. Based on initial
analyses suggesting higher cover clusters have reefs with greater depths, we constrain the
$\beta_{depth}$ coefficient prior to positive values. Similarly, we constrain the
$\beta_{DHW}$ coefficient prior to negative values as we do not expect increasing DHW levels to
increase cluster assignment level.

>>>>

We used a multinomial linear regression model to quantify the influence of reef
characteristics on reef cluster assignment. We model the
influence of seven predictors, median depth, log total connectivity strength, log source to
sink ratio, mean DHW, log reef area, mean DHW tolerance level and GCM on cluster assignment.
